### 2004-09-13 Documentation/Manual.tex
Fixed a minor bug in XCC_CNGS.dat (it contained a spurious newline)
Affiliation updated

\newcommand{\glbxxx}{hep-ph/0407xxx}
\newcommand{\capdef}{}
\newcommand{\mycaption}[2][\capdef]{\renewcommand{\capdef}{#2}%
        \caption[#1]{{ %\itshape
 {\footnotesize #2}}}}
\makeatletter
\renewcommand{\fnum@table}{\textbf{\tablename~\thetable}}
\renewcommand{\fnum@figure}{\textbf{\figurename~\thefigure}}
\makeatother

@@

{\em\small $^{\mathrm{a},\mathrm{b},\mathrm{c}}$%
       Institut f\"ur Theoretische Physik, Physik--Department,\\
       Technische Universit\"at M\"unchen,
       James--Franck--Strasse, D--85748 Garching, Germany}

@@

\vspace*{-2ex}
\GLOBES\ (``General Long Baseline Experiment Simulator'') is a flexible
software package to simulate neutrino oscillation 
long baseline and reactor experiments. On the
one hand, it contains a comprehensive abstract experiment definition
language (AEDL), which allows to describe most classes 
of long baseline experiments
at an abstract level. On the other hand, it provides a C-library to 
process the experiment information in order to obtain oscillation
probabilities, rate vectors, and $\Delta \chi^2$-values. Currently, 
\GLOBES\ is available for GNU/Linux. Since the source code is included,
the port to other operating systems is in principle possible.

>>>>

\newcommand{\glbxxx}{hep-ph/0407333}
\newcommand{\capdef}{}
\newcommand{\mycaption}[2][\capdef]{\renewcommand{\capdef}{#2}%
        \caption[#1]{{ %\itshape
 {\footnotesize #2}}}}
\makeatletter
\renewcommand{\fnum@table}{\textbf{\tablename~\thetable}}
\renewcommand{\fnum@figure}{\textbf{\figurename~\thefigure}}
\makeatother

@@

{\em\small $^{\mathrm{a},\mathrm{b}}$%
       Institut f\"ur Theoretische Physik, Physik--Department,\\
       Technische Universit\"at M\"unchen,
       James--Franck--Strasse, D--85748 Garching, Germany}

{\em\small $^{\mathrm{c}}$%
       Institute for Advanced Study, 
       Einstein Drive, Princeton, NJ 08540, USA}

@@

\vspace*{-4ex}
\GLOBES\ (``General Long Baseline Experiment Simulator'') is a flexible
software package to simulate neutrino oscillation 
long baseline and reactor experiments. On the
one hand, it contains a comprehensive abstract experiment definition
language (AEDL), which allows to describe most classes 
of long baseline experiments
at an abstract level. On the other hand, it provides a C-library to 
process the experiment information in order to obtain oscillation
probabilities, rate vectors, and $\Delta \chi^2$-values. Currently, 
\GLOBES\ is available for GNU/Linux. Since the source code is included,
the port to other operating systems is in principle possible. The software
as well as up-to-date versions of this manual can be found at this URL:
 \verb+http://www.ph.tum.de/~globes+
